True Stellar Obliquity Distribution of Exoplanets

### 2022-11-15 src/tex/ms.tex
[showyourwork] overleaf sync

@@

>>>>

\received{}
\revised{}
\accepted{}

\submitjournal{AAS Journals}

@@

Stellar obliquity $\psi$ is described as the angle between a planet's orbital axis $\hat{i}_{\rm orb}$ and its host star's spin axis $\hat{i}_{\star}$. If both $\hat{i}_{\rm orb}$ and $\hat{i}_{\star}$ are random unit vectors with uniform distribution on a three-dimensional sphere, $\cos{\psi}$ will be uniformly distributed between $-1$ and 1.

\begin{figure}[ht!]
    \script{hbm_istar.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/hbm_istar.pdf}
        \caption{Plot showing a bunch of random numbers.}
        \label{fig:hbm_istar}
    \end{centering}
\end{figure}

\begin{figure}
    \script{hbm_all.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/hbm_all.pdf}
        \caption{Plot showing a bunch of random numbers.}
        \label{fig:hbm_all}
    \end{centering}
\end{figure}
